### 2024-06-24 basic-statistics.qmd
20240623 - tweaks

Two-samples *t*-tests are used to test for differences between scores of two groups.
If the two groups are independent, the independent samples *t*-test is used.
If the two groups involve paired samples, the paired samples *t*-test is used.
For instance, you could use an independent-samples *t*-test if you want to examine whether Quarterbacks tend to have have longer careers than Running Backs.
By contrast, you could use a paired samples *t*-test if you want to examine whether Quarterbacks tend to score more points in the second year of their contract compared to their rookie year, because the same subjects were assessed twice (i.e., a [within-subject designs](#sec-withinSubject)).

@@

Regression with multiple predictors takes the following form:

>>>>

Two-samples *t*-tests are used to test for differences between scores of two groups.
If the two groups are independent, the independent samples *t*-test is used.
If the two groups involve paired samples, the paired samples *t*-test is used.
For instance, you could use an independent-samples *t*-test if you want to examine whether Quarterbacks tend to have have longer careers than Running Backs.
By contrast, you could use a paired samples *t*-test if you want to examine whether Quarterbacks tend to score more points in the second year of their contract compared to their rookie year, because the same subjects were assessed twice (i.e., a [within-subject design](#sec-withinSubject)).

@@

Regression with multiple predictors—i.e., multiple regression—takes the following form:
